Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
sec 4

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning, \cf Fig.~\ref{fig:fusion_abiguty}.
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
\mathcal{E}_0  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0$.
%
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0 \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
%\begin{align}
%  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
%\end{align}
%

>>>>

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion}\label{sec:cc_fm}

Fusion move algorithms~\cite{Lempitsky-2010} are a popular technique 
for large scale discrete energy minimization problems.
They iteratively fuse two node labelings by optimizing over the label space spanned by those.
Different fusion algorithms vary in the proposals and method used for the auxiliary fusion problem~\cite{kappes_2014_ws}.

As fusion algorithms work with node labelings, % \cf Eq.~\ref{eq:nodeproblem},
we face the problem that the node coloring is ambiguous and has no semantic meaning.
This causes that a fusion move is not well defined, because different choices of colors 
lead to different auxiliary problems, as shown in Fig.~\ref{fig:fusion_abiguty}.

In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{E}^0_{\breve{y}}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
\mathcal{E}^0_{\breve{y}}  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{E}^0_{\breve{y}}$.
%
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}^0_{\breve{y}} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
%\begin{align}
%  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
%\end{align}
%
